\section{Baseline Three-Equation NK Model}

Let \(x_t\) denote the output gap, \(\pi_t\) inflation, \(i_t\) the nominal
policy rate, and \(r^n_t\) the natural real rate. The standard first-order
three-equation New Keynesian system is
\begin{align}
    x_t
    &=
    \E_t x_{t+1}
    -
    \frac{1}{\gamma}
    \left(
        i_t - \E_t \pi_{t+1} - r^n_t
    \right),
    \label{eq:baseline_is}
    \\
    \pi_t
    &=
    \beta \E_t \pi_{t+1}
    +
    \kappa x_t,
    \label{eq:baseline_nkpc}
    \\
    i_t
    &=
    \rho_i i_{t-1}
    +
    (1-\rho_i)
    \left(
        \phi_\pi \pi_t + \phi_x x_t
    \right)
    +
    \varepsilon^i_t.
    \label{eq:baseline_taylor}
\end{align}
The parameters satisfy \(\gamma>0\), \(0<\beta<1\), \(\kappa>0\), and
\(0\leq \rho_i<1\). In the baseline accounting exercise, monetary policy is not
a primitive uncertainty source, so \(\varepsilon^i_t\) is set to zero unless the
policy rule is used as a residual measurement equation.

Productivity enters the reduced-form NK system through the natural allocation.
For example, in a flexible-price economy with log productivity \(a_t\), natural
output and the natural real rate can be summarized as
\begin{align}
    y^n_t &= \chi_a a_t,
    \label{eq:natural_output}
    \\
    r^{n,1}_t
    &=
    \rho
    +
    \gamma \E_t \Delta y^n_{t+1},
    \label{eq:first_order_natural_rate}
\end{align}
where \(\rho=-\log\beta\), \(\chi_a\) is the elasticity of natural output with
respect to productivity, and \(r^{n,1}_t\) is the first-order natural real rate.
Second-order risk corrections will modify this object. The notation
\(r^{n,1}_t\) is used to keep the first-order natural rate conceptually separate
from the risk-adjusted natural rate.

\begin{remark}
Equations \eqref{eq:baseline_is}--\eqref{eq:baseline_taylor} are already
log-linear. Therefore, uncertainty effects do not arise by simply changing the
variance of \(a_t\) inside these equations. The risk terms must come from a
second-order expansion of the nonlinear household and firm conditions that
generate the reduced-form NK system.
\end{remark}
